\bf Model Visualization Techniques for a Social Network Model

### 2017-06-02 paper.Rnw
next paragraph

The parameters, $\boldsymbol{\beta}$, are attached to various actor-level network statistics, $s_{ik}(x)$. \hh{'There are always' ... that seems to come from a Snijder paper? Re-phrase this to be less vague: In the current implementation of RSiena (snijder) a model has minimally two parameters...} There are always at least two parameters, $\beta_1$ for the outdegree of a node, and $\beta_2$ for the number of reciprocal ties held by a node \citep[p. 371]{snijders01}. \hh{'There are many' another vague phrase} There are many possible parameters $\beta_i$ to add to the model. \hh{'They' ... be specific.} They can be split up into two groups: first, the structural effects, which only depend on the structure of the network. \sct{The inclusion of these effects has origin in the classical exponential random graph model (ERGM) for networks. These effects are written in terms of the edge variables $x_{ij}$, for $i \neq j$. The second set of effects are the actor-level or covariate effects.} \hh{XXX move the last colored section to the front of this paragraph. That sets up the structure nicely, e.g. `In determining the covariates of a SAOM, two sources of parameters are considered: ...} These effects also depend on the structure of the network. They are written in terms of $x_{ij}$ but also in terms of the covariates, $\mathbf{Z}$. A table of some possible structural and covariate effects is given in Table~\ref{tab:effects}. For a complete list of the network and covariate statistics that can be included \hh{currently} in the objective function, see \citet{RSiena}.

@@

When node $i$ is given the chance to change a tie, we assume that they wish to maximize the value of their objective function $f_i(\boldsymbol{\beta}, x)$ plus a random element, $U_i(x)$, where the $U_i(x)$ are from "the type 1 extreme value distribution (or Gumbel distribution) with mean 0 and scale parameter 1" \citep[p. 368]{snijders01}. This distribution, which is also known as the log-Weibull distribution, has probability distribution function, using $\mu$ for the mean parameter and $\sigma$ for the scale parameter, of

@@

>>>>

The parameters, $\boldsymbol{\beta}$, are attached to various actor-level network statistics, $s_{ik}(x)$. \hh{'There are always' ... that seems to come from a Snijder paper? Re-phrase this to be less vague: In the current implementation of RSiena (snijder) a model has minimally two parameters...} There are always at least two parameters, $\beta_1$ for the outdegree of a node, and $\beta_2$ for the number of reciprocal ties held by a node \citep[p. 371]{snijders01}. \hh{'There are many' another vague phrase} There are many possible parameters $\beta_i$ to add to the model. \hh{'They' ... be specific.} They can be split up into two groups: first, the structural effects, which only depend on the structure of the network. \st{The inclusion of these effects has origin in the classical exponential random graph model (ERGM) for networks. These effects are written in terms of the edge variables $x_{ij}$, for $i \neq j$. The second set of effects are the actor-level or covariate effects.} \hh{XXX move the last colored section to the front of this paragraph. That sets up the structure nicely, e.g. `In determining the covariates of a SAOM, two sources of parameters are considered: ...} These effects also depend on the structure of the network. They are written in terms of $x_{ij}$ but also in terms of the covariates, $\mathbf{Z}$. A table of some possible structural and covariate effects is given in Table~\ref{tab:effects}. For a complete list of the network and covariate statistics that can be included \hh{currently} in the objective function, see \citet{RSiena}.

@@

When node $i$ is given the chance to change a tie, \hh{`we assume that they wish' sounds strange - don't assume wishes, state assumptions} we assume that they wish to maximize the value of their objective function $f_i(\boldsymbol{\beta}, x)$ plus a random element, $U_i(x)$, where the $U_i(x)$ are from \hh{XXX don't cite here - just state that Snijder suggest the use of a type 1 extreme value distribution on top of the objective function. XX What is the thought behind that? } ``the type 1 extreme value distribution (or Gumbel distribution) with mean 0 and scale parameter 1" \citep[p. 368]{snijders01}. This distribution, which is also known as the log-Weibull distribution, has probability distribution function, using $\mu$ for the mean parameter and $\sigma$ for the scale parameter, of

@@

\hh{This paragraph ends a bit abruptly - what is the future state probability used for?}
